A novel 1000\,MW double-reheat ultra-supercritical system with turbine-extraction-heated air preheaters and low-temperature economizers

### 2018-04-25 article.tex
继续修改引言部分

 为了能够提高热电厂的循环效率，研究人员不断对火电厂系统进行改进优化。
 Sven Kjaer et al.~\cite{Kjaer2010A} considered that those investigations can be grouped along three side tracks, i.e. the temperature track, which employs higher live steam parameters such as 30-35 MPa, above 700$^\circ$C in the future~\cite{Bugge2014High}, the component track, which improves the efficiency of key equipment such as boiler~\cite{Rosen2008Improving} and turbine~\cite{Zhang2016Optimization}, and the Carnot track, which makes efforts to reduce the defection of the real cycle of the power plant~\cite{Liu2018}.

对锅炉烟气余热的利用一直以来都是系统优化的重点。近年来部分学者提出的利用锅炉烟气加热给水方法提高系统效率，在该思路的指导下多种系统形式被提出：

@@

二次再热也已经作为一种有效提高系统效率的方式被深入研究并进行深入分析：

To identify reasonable reheat parameters, Zhou et al.~\cite{Zhou2016Parametric} carried out a parametric analysis and system optimization of double-reheat ultra-supercritical power plants based on exergy analysis and economic analysis. The results showed that reasonable reheat parameters and reheat stage numbers can improve the double-reheat system's performance.

To reduce the superheat degree of the extractions, Xu et al.~\cite{Xu2015Optimum} investigated the thermal performance of the steam and water cycle with a single reheat after the installation of an additional outer steam cooler (AOC).
The results showed that the AOC is an effective method of reducing the superheat degree and improving the efficiency of the unit.
Li et al.~\cite{Li2014Thermodynamic} proposed a system that uses ten-stage extractions and two outer steam coolers. 
The results of the thermodynamic and Technical-economic analyses showed that this system can lower the cost of electricity to 55.89 USD/MWh.
In addition, Kjaer~\cite{Kjaer2010A} proposed a regenerative steam turbine for utilizing the superheat degree of the extractions.
In this design, part of the extraction from the turbine high pressure cylinder enters the additional regenerative steam turbine rather than the regenerative heater.
Extractions from the turbine intermediate pressure cylinder are replaced by those from the regenerative steam turbine.
The superheat degree of the extraction is significantly reduced in this design and the exergy destruction of regenerative heaters is likewise reduced, thereby resulting in an overall improvement in efficiency.

@@

% Though the high live steam pressure and temperature of the USC unit improve its efficiency, there are still some imperfections that limit the improvement of the unit's performance. 
为了能够对系统进行更加进一步的优化，用分析的方法被应用到热力系统优化中
In order to perform an in-depth analysis of the system, Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double-reheat USC power plant and determined the main causes of exergy destruction on the steam turbine.
Rashidi et al.~\cite{Rashidi2014Thermodynamic} performed a thermodynamic analysis of a double-reheat steam power plant.
According to Ref.~\cite{Wu2014Component}, component- and process-based exergy evaluations were performed on a coal-fired power plant in China, thereby helping researchers to identify energy-saving strategies.
It was pointed out that the exergy destruction in the heat transfer process accounts for the largest proportion of exergy destruction overall.

现有研究往往关注与烟气余热温度与给水温度相匹配，并没有对锅炉中原有受热面进行优化。而通过火用分析，热力系统中锅炉损失占总用损失的70%，空预器的损失和整个回热系统的损失相当。
通过实现空气、汽轮机抽汽、锅炉省煤器出口烟气和冷凝水温度相匹配，够降低低锅炉用损失，提高系统效率。
这一点对于二次再热系统尤为重要，随着近年来二次再热机组在世界范围研究和投入使用，其高效收到的广泛的认可，但是由于再热后抽汽的过热度提高，导致抽汽和给水温度不匹配造成的用损失也更加显著。
所以在二次再热机组上进行多工质温度匹配分析对机组节能更具有潜力。

>>>>

In order to improve the power generation efficiency of thermal power plants, researchers have carried out a number of investigations.
Sven Kjaer et al.~\cite{Kjaer2010A} considered that those investigations can be grouped along three side tracks, i.e. the temperature track, which employs higher live steam parameters such as 30-35 MPa, above 700$^\circ$C in the future~\cite{Bugge2014High}, the component track, which improves the efficiency of key equipment such as boiler~\cite{Rosen2008Improving} and turbine~\cite{Zhang2016Optimization}, and the Carnot track, which makes efforts to reduce the defection of the real cycle of the power plant~\cite{Liu2018}.

Among the methods of optimzing the thermal cycle of power plant, the double-reheat USC unit is attractiong increasing number of attention and developing rapidly worldwide. 
The double-reheat USC unit is a new generation of USC unit that can improve thermal performance when compared with a single reheat unit. 
According to~\cite{Zhao2017Exergy}, a double-reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\% when compared with a commonly used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
The United States built the first double-reheat unit with the main parameter 34.4 MPa/649/566/566$^\circ$C in the 1960s.
Two 700 MW double-reheat USC units were put into operation in Japan in 1990. 
The process of building five double-reheat USC units began in China in 2012, and three of these units were put into operation in 2015.

Although the double-reheat USC unit can improve the system efficiency, it also bring some other problems, such as the superheat degree of extractions after first- and second- reheater are extremly high which cause high exergy lose of regenerative heaters. 
And the increased volume flow after second-reheater needs extra-large low-pressure cylinder~\cite{nicol2015application}.

Liu et al.~\cite{Liu2017} investigated a 660 MW double-reheat unit and calculated the coal consumption decrease if the overheats of No.5 to No.10 extractions could be recovered.
Wang et al.~\cite{Wang2016} studied 1000MW double-reheat USC system adopting outer steam coolers to utilize the superheat of extraction steam and the influence of different extraction schemes on system efficiency.
% Zhou et al.~\cite{Zhou2016Parametric} carried out a parametric analysis and system optimization of double-reheat ultra-supercritical power plants based on exergy analysis and economic analysis. 
% The results showed that reasonable reheat parameters and reheat stage numbers can improve the double-reheat system's performance.
% Xu et al.~\cite{Xu2015Optimum} investigated the thermal performance of the steam and water cycle with a double reheat after the installation of an additional outer steam cooler (AOC).
The results showed that the AOC is an effective method of reducing the superheat degree and improving the efficiency of the unit.
Li et al.~\cite{Li2014Thermodynamic} proposed a system that uses ten-stage extractions and two outer steam coolers. 
The results of the thermodynamic and technical-economic analyses showed that this system can lower the cost of electricity to 55.89 USD/MWh.
In addition, Kjaer~\cite{Kjaer2010A} proposed a regenerative steam turbine for utilizing the superheat degree of the extractions.
In this design, part of the extraction from the turbine high pressure cylinder enters the additional regenerative steam turbine rather than the regenerative heater.
Extractions from the turbine intermediate pressure cylinder are replaced by those from the regenerative steam turbine.
The superheat degree of the extraction is significantly reduced in this design and the exergy destruction of regenerative heaters is likewise reduced, thereby resulting in an overall improvement in efficiency.
Xu et al.~\cite{Xu2015Optimum} compared two superheat utilization systems, one is with additional outer steam cooler (AOC) and the other one is with regenerative steam turbine.
The results showed that the system with regenerative steam turbine had a better techno-economic performance.

%虽然能够对蒸汽过热度进行利用，但是回热系统中换热器温差依旧很大。而利用锅炉烟气加热给水能够减少回热系统的换热温差

%对锅炉烟气余热的利用一直以来都是系统优化的重点。近年来部分学者提出的利用锅炉烟气加热给水方法提高系统效率，在该思路的指导下多种系统形式被提出：

@@

现有研究往往关注与烟气余热温度与给水温度相匹配，并没有对锅炉中原有受热面进行优化。
为了能够对系统进行更加进一步的优化，用分析的方法被应用到热力系统优化中
In order to perform an in-depth analysis of the system, Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double-reheat USC power plant and determined the main causes of exergy destruction on the steam turbine.
Rashidi et al.~\cite{Rashidi2014Thermodynamic} performed a thermodynamic analysis of a double-reheat steam power plant.
According to Ref.~\cite{Wu2014Component}, component- and process-based exergy evaluations were performed on a coal-fired power plant in China, thereby helping researchers to identify energy-saving strategies.
It was pointed out that the exergy destruction in the heat transfer process accounts for the largest proportion of exergy destruction overall.

而通过火用分析，热力系统中锅炉损失占总用损失的70%，而空预器的损失和整个回热系统的损失相当。
降低空预器的用损失是实现系统用效率提升的重点
通过实现空气、汽轮机抽汽、锅炉省煤器出口烟气和冷凝水温度相匹配，够降低低锅炉用损失，提高系统效率。
这一点对于二次再热系统尤为重要，
所以在二次再热机组上进行多工质温度匹配分析对机组节能更具有潜力。

@@

% Though the high live steam pressure and temperature of the USC unit improve its efficiency, there are still some imperfections that limit the improvement of the unit's performance.
